### 2014-06-27 Choosing R3 Relations.tex
Added Lemma 4.6

>>>>

\begin{lem} (Analogue of 4.6) 
Let W$_{\Gamma}$ be generated by $s_{1}, \dots, s_{n}$. Then $s_{1}^{-1}, \dots, s_{n}^{-1}$ satisfy the relations (R2') and (R3') in W$_{\Gamma^{op}}$.
\end{lem}
\begin{proof}
One can see that the elements satisfy (R2') in W$_{\Gamma^{op}}$ by taking the inverse of both sides of the relation in W$_{\Gamma}$. To see that the elements satisfy (R3') in W$_{\Gamma^{op}}$, note that for a chordless cycle in $\Gamma$ with all weights equal to one, we have $$s_{0}^{-1}\dots s_{d-2}^{-1}s_{d-1}s_{d-2}\dots s_{0} = s_{1}^{-1}\dots s_{d-2}^{-1}s_{d-1}s_{d-2}\dots s_{1}$$ by the relation r(0,1) in (R3') in W$_{\Gamma}$. But then applying relations from (R2'), we have that $$s_{0}^{-1}\dots s_{d-1}s_{d-2}s_{d-1}^{-1}\dots s_{0} = s_{1}^{-1}\dots s_{d-1}s_{d-2}s_{d-1}^{-1}\dots s_{1},$$ and since the cycle in chordless, we then have $$s_{0}^{-1}s_{d-1}\dots s_{d-3}^{-1}s_{d-2}s_{d-3}\dots s_{d-1}^{-1}s_{0} = s_{d-1}s_{1}^{-1}\dots s_{d-3}^{-1}s_{d-2}s_{d-3}\dots s_{1}s_{d-1}^{-1}.$$ Repeating this process, we find that $$s_{0}^{-1}s_{d-1}s_{d-2}\dots s_{2}s_{1}s_{2}^{-1}\dots s_{d-2}^{-1}s_{d-1}^{-1}s_{0} = s_{d-1}s_{d-2}\dots s_{2}s_{1}s_{2}^{-1}\dots s_{d-2}^{-1}s_{d-1}^{-1}.$$ But this can only occur if $s_{1}^{-1}, \dots, s_{n}^{-1}$ satisfies the relation r(0, d-1) in W$_{\Gamma^{Op}}.$ Therefore, we are done.
\end{proof}
